### 2023-01-27 README.Rmd
...

The **cols4all** is a new R package for selecting color palettes. "Color for all" refers to our mission that colors should be usable for not just people with normal color vision, but also for people with color vision deficiency. Currently, this package contains palettes from several popular and lesser known color palette series: [Color Brewer](https://colorbrewer2.org), [Viridis](http://bids.github.io/colormap/), [Kovesi](https://colorcet.com/), [Paul Tol](https://personal.sron.nl/~pault/), [Scico](https://www.fabiocrameri.ch/colourmaps/), [Carto](https://carto.com/carto-colors/), [Tableau](https://www.tableau.com/about/blog/2016/7/colors-upgrade-tableau-10-56782), [Wes Anderson](https://github.com/karthik/wesanderson), and [Seaborn](https://seaborn.pydata.org/tutorial/color_palettes.html). Own palettes series can be added as well.

@@

What palettes are available?

```{r, output.lines = 10}
# All loaded palettes
c4a_palettes()
```

@@

```{r}
# Select the palette "kelly" with 7 colors
c4a("kelly", 7)

# select purple green palette from the hcl series:
c4a("hcl.purple_green", 11)

@@

@@

*   `c4a_gui` Dashboard for analyzing the palettes
*   `c4a` Get the colors from a palette

>>>>

The **cols4all** is a new R package for selecting color palettes. "Color for all" refers to our mission that colors should be usable for not just people with normal color vision, but also for people with color vision deficiency. Currently, this package contains palettes from several popular and lesser known color palette series. Own palettes series can be added as well.

@@

What types and series are available?

```{r}
c4a_types()

c4a_series()
```

How many palettes per type x series?

```{r}
c4a_overview()
```

What palettes are available, e.g diverging from the hcl series?

@@

```{r}
# select purple green palette from the hcl series:
c4a("hcl.purple_green", 11)

@@

Plot these colors:

```{r, fig.height = 2}
c4a_plot("hcl.purple_green", 11, include.na = TRUE)
```

## Using cols4all palettes in ggplot2

```{r}
library(ggplot2)
data("diamonds")
diam_exp = diamonds[diamonds$price >= 15000, ]

# discrete categorical scale
ggplot(diam_exp, aes(x = carat, y = price, color = color)) +
	geom_point(size = 2) +
	scale_color_discrete_c4a_cat("carto.safe") +
	theme_light()

# continuous diverging scale
ggplot(diam_exp, aes(x = carat, y = depth, color = price)) +
	geom_point(size = 2) +
	scale_color_continuous_c4a_div("wes.zissou1", mid = mean(diam_exp$price)) +
	theme_light()
```

@@

*   `c4a_gui` Dashboard for analyzing the palettes
*   `c4a` Get the colors from a palette (`c4a_na` for the associated color for missing values)
*	`c4a_plot` Plot a color palette
